\documentclass[11pt,letterpaper]{moderncv}
\usepackage[utf8]{inputenc}
\moderncvstyle{casual}          % casual banking
\moderncvcolor{green}
\moderncvicons{awesome}

\usepackage[scale=0.75,margin=0.7in]{geometry} % showframe
\setlength{\hintscolumnwidth}{2.5cm}

% Hyperlinks
\usepackage[unicode]{hyperref}           % to use hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % hyperlinks setup
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname {Tobias}
\familyname {Tripp}

\email{toby@tripp.net}
\social[github]{tobytripp}
% \social[twitter]{tobytripp}

\begin{document}
\makecvtitle

\section{Profile}

\begin{minipage}{\textwidth}
  \setlength{\hintscolumnwidth}{0pt}
  \setlength{\maincolumnwidth}{\textwidth-1cm}
  \subsection{I Value:}
  \begin{cvcolumns}
    \cvcolumn[0.4]{Outcomes}{%
      \begin{itemize}%
      \item \emph{Practice over Heroics}
      \item \emph{Gently exceed customer expectations}
      \item \emph{There is} always \emph{more to learn}
      \item \emph{Collaboration over Competition}
    \end{itemize}}
    \cvcolumn{Supported by}{%
      \begin{itemize}%
      \item \emph{Fast, dependable, automated tests} quickly direct the
        developer to problems and document the system.
      \item \emph{Automated build and deployment} cycle rapidly between
        conception and delivery, with True \emph{Continuous
          Integration} for release decisions without constraint.
      \item \emph{Iterative designs} grow solutions to complex problems
        from simple components.
      \item \emph{Pair-Programming} maximizes peer-review
        and shares knowledge.
      \item \emph{Test-Driven Development} toward solid design, complete tests,
        and confident development.
    \end{itemize}}
  \end{cvcolumns}
\end{minipage}

\begin{minipage}{\textwidth}
  \setlength{\hintscolumnwidth}{0pt}
  \subsection{Skills}
\end{minipage}

\cvitemwithcomment{Proficient}{\small Ruby, Clojure, Javascript}{}
\cvitemwithcomment{Professional}{\small Ada, Java, C, C++, Perl, Tcl/Tk, Php,
  Soar} {\tiny also Awk and Ksh, but that's a story\ldots}
\cvitemwithcomment{Hobbyist}{\small Haskell, Prolog, Elm, MiniKanren}{}

\section{Experience}

%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{January 2024-\\November 2025} {Engineering Lead/Manager} {Ignite
  Reading} {Remote} {} { %
  Ignite is a mission-driven organization taking on the ongoing literacy
  crisis in America.  Ignite uses one-on-one virtual tutoring and a
  science-based curriculum to help children learn to read.
  \begin{itemize}
  \item Worked with engineers at all levels of the software lifecycle, from
    design to quality engineering.
  \item Helped improve the skills of fellow engineers by working closely with
    them, presenting educational materials and code katas, and providing
    consistent and immediate feedback.
  \item Planned, architected, and implemented full-stack features.
  \item “Helping the team navigate some challenging terrain, and always
    delivering features on time.  By challenging terrain, I mean a rapidly
    changing product roadmap and short lead times for feature delivery.  [...]
    Toby has taken it all in stride, never complaining but rather responding
    and delivering.”
  \item “Toby has recruited, hired, and onboarded several strong Software
    Engineers [...].  In fact, all software engineers on Croissant are folks
    Toby has brought into the organization.  The Croissant team seems to be at
    full strength and working on good stride.”
  \item “Toby has built an environment on trust and empowerment, which is felt
    and appreciated by the team.  It's clear Toby wants the effort and credit
    to fall to the folks doing the work, and creates a great support and
    collaboration model with pair programming practices.”
  \item “Toby is patient and calm, even during busy times. Team members see
    this and appreciate his ‘slow and smooth’ demeanor, which is an excellent
    model for others.”
  \end{itemize}
  Skills: \emph{Management, Agile / Scrum / XP, Ruby, Rails, React, JavaScript}
}

\cventry{September 2021-\\November 2022} {Engineering Lead} {Provi} {Chicago,
  Illinois} {} { %
  Provi simplifies the complex process of ordering, selling and promoting
  wholesale alcohol between buyers, distributors and suppliers.  At Provi, I:
  \begin{itemize}
  \item managed a team of nine software developers of varying experience
    levels.
  \item mentored team members through Agile practices such as TDD and
    Pair-programming.
  \item oversaw architecture and design for Ruby on Rails and Javascript
    Svelte code bases.
  \end{itemize}
  Skills: \emph{Management, Agile / XP, Ruby, Rails, Svelte.js, JavaScript}
}

\cventry{September 2019-\\September 2021} {Senior Software Developer and Team Co-Lead}
  {OppLoans} {Chicago, Illinois} {} { %
  OppLoans is a leading fintech platform that powers banks to help middle
  income, credit-challenged consumers.  At OppLoans, I:
  \begin{itemize}
  \item continually helped the team improve its development and delivery
    process.
  \item applied agility and design to the Ruby on Rails front-end and to its
    supporting services.
  \item worked with team members to develop a culture of continuous learning.
    \begin{itemize}
    \item ``Toby is the type of person that when he commits to something, it
      will get done.''
    \item ``Toby is always super helpful to everyone on the dev team.  When
      people are stuck on something, he always offers to jump in and take a
      look.  He does a really good job of sharing his knowledge around Rails
      and Ruby, so we all learn a lot from him.''
    \end{itemize}
  \end{itemize}
  Skills: \emph{Management, Agile / XP, Ruby, Rails, Clojure, React, JavaScript}
}

\cventry{June 2018-\\September 2019} {Lead Software Developer}
  {OpenMarkets Health} {Chicago, Illinois} {} { %
  OpenMarkets is a rapidly growing technology company reinventing the
  healthcare equipment marketplace with an emphasis on data, collaboration,
  and simplicity.  While at OpenMarkets, I:
  \begin{itemize}
  \item led the team in developing a new deployment process that allowed more
    frequent and responsive deployment of features to production.
  \item led and trained the team in desiging and developing the Clojure
    back-end and ClojureScript front-end of the OpenMarkets platform.
  \item helped the team develop an effective strategy for remote
    pair-programming.
  \end{itemize}
  Skills: \emph{Management, Agile / XP, Clojure, ClojureScript}
}

\cventry{May 2015-\\January 2018} {Lead Software Developer} {Goldstar
  Learning} {Chicago, Illinois} {} { %
  Goldstar produces \href{https://www.masterymanager.com}{masterymanager.com},
  an assessment and reporting tool for K-12 teachers and administrators.  Once
  administered, educators can produce a set of reports to demonstrate the
  efficacy of the material being taught or of the assessment itself.  While at
  Goldstar, I:
  \begin{itemize}
  \item led the initiative to migrate mastery-manager's current decade-old
    monolithic Perl system into smaller redesigned sub-systems.
  \item instructed developers--with widely varying experience
    levels--in Object-Oriented software design, systems architecture,
    and planning.
  \item began the creation of a new Clojure reporting system that will allow
    for real-time assessment result reporting.  Reporting results are
    presented in a set of interactive d3.js views.  Used generative tests
    with \href{https://github.com/clojure/test.check}{test.check} to reduce
    defects.
  \end{itemize}
  Skills: \emph{Leadership, Agile / XP, Ruby, Rails, Clojure, Perl, JavaScript}
}

\cventry{December 2010--\\May 2015} {Senior Developer} {Backstop Solutions Group} {Chicago, Illinois} {} {%
  Backstop is an award-winning software provider that creates solutions for a
  wide variety of fund managers.  I worked on the InvestorBridge platform: a
  Rails application that integrates with Backstop's Java CRM platform to
  provide an information portal for fund managers to more easily release
  information to their investors.
  \begin{itemize}
  \item shared expertise company-wide in such areas as Agile planning,
    developer testing, Object-Oriented design principles, Javascript
    and Ruby fundamentals, performance analysis and optimization,
    debugging, configuration management, and general software design.
  \item coached developers through the practice of pair-programming.
  \item gave a number of classes in these areas.
  \item led the team in the development of a Clojure/Datomic back-end for encoding the
    complicated permissions applied to InvestorBridge resources.
  \end{itemize}
  Skills: \emph{Leadership, Agile / XP, Ruby, Rails, Java, Clojure, JavaScript}
}

\cventry{April 2007--\\December 2010} {Senior Consultant} {ThoughtWorks} {Chicago, Illinois} {} {%
  ThoughtWorks is a global software consultancy with a focus on Agile software
  delivery and client enablement. While at ThoughtWorks, I was involved with
  the following clients:}
\begin{list}{\labelitemi}{
    \normalfont
    \small
    \setlength{\leftmargin}{3.2cm}
    \setlength{\topsep}{0cm}
    \setlength{\itemsep}{0cm}
    \setlength{\parsep}{0cm}}
\item \emph{Major Political Party}: Created a high-performance national
  voter lookup service to aid their collaborators in sharing voter
  information and with locating and de-duplicating their large
  database. The service is implemented as a Ruby Rack endpoint in
  front of a MongoDB database. Also created a similar service in
  Sinatra for reserving voters with an iPhone canvassing application.
\item \emph{Major Labor Union}: As part of a new program to organize
  and train 10,000 of their members, led a team to create a
  social-networking platform to support collaboration and involvement.
  The site is implemented in Ruby on Rails and tested with RSpec and
  Cucumber. It is deployed on Passenger.
\item \emph{Oracle Mix}: designed, developed, and deployed
  mix.oracle.com in a compressed engagement of 5 weeks and two
  developers, working closely with Oracle Labs to iteratively deliver
  a new customer engagement site for Oracle customers. The site claims
  to be the first enterprise deployment of JRuby on Rails for customer
  consumption.
\item \emph{Sleepy Giant}: near the beginning of Sleepy Giant's
  business, I helped coach the company through requirements gathering
  and categorization as well as coaching the developer through his
  early practice of Test-Driven Development.
\item \emph{Leading VOIP Provider}: worked as a developer on the team
  that rewrote the company's legacy J2EE front- end customer
  subscription system in Ruby on Rails. Following an initial
  production release, the team released to production every eight
  weeks with new features the client had been unable to add to the
  legacy system without introducing intractable regression issues. At
  last count, the site handled more than 200,000 hits a day and
  integrated with 2 legacy databases and more than 20 web services.
\item \emph{A Leading Wholesale Auto Auction}: This was the largest
  Ruby on Rails project to be undertaken anywhere in the world. The
  domain involved working on an auction site for trading automobiles
  which included many custom features for sellers. Helped on this team
  as a Ruby on Rails developer to build stories and get this project
  finished ahead of time. Involved in TDD with RoR, integrating RoR
  applications with web-services (written in Java), and functional
  integration testing with Selenium and Ruby.
\end{list}
\begin{list}{}{\small\setlength{\leftmargin}{3.2cm}\setlength{\topsep}{0cm}}
  \item Skills: \emph{Leadership, Agile / XP, Ruby, Rails, Java, Groovy, JavaScript}
\end{list}


\cventry{November 2006--\\January 2007}  {Software Development Consultant} {Menlo Innovations} {Ann Arbor, Michigan} {} {%
  Menlo Innovations builds software for a very diverse client set using High
  Tech Anthropology\textregistered \ and Extreme Programming.  Projects
  included a web based system to ease the viewing of compound testing results
  for a large pharmaceutical company and software to power a flow-cytometer
  for a small Ann Arbor firm.\newline During this brief but valuable engagement, I
  was able to:
  \begin{itemize}
  \item mentor junior developers in Object Oriented Design and in
    automated testing.
  \item contribute to architecture discussions and decisions.
  \end{itemize}
  Skills: \emph{Mentorship, Agile / XP, Java}
}

\cventry {July 2005--\\November 2006} {Software Engineer} {Soar Technology} {Ann Arbor, Michigan} {} {%
  Soar Technology develops and researches cognitive software for application
  in training, modeling \& simulation, intelligence analysis, command and
  control, robotics, and medical informatics.\newline While at Soar, I:
  \begin{itemize}
  \item Developed tools and systems to apply artificial intelligence
    technology to simulation, modeling, and user interface design.
  \item Created custom IDE applications on top of the Eclipse platform.
  \item Developed and maintained tools, using Java Swing and SWT, for
    visualizing the state and actions of AI agents. This included
    mapping, event table, and agent interaction visualizations.
  \item Instigated the deployment and use of multi-platform
    continuous integration practices.
  \item Integrated several diverse systems, including an agent
    component in Soar, to model complex social networks.
  \item Advocated for, and helped implement, an open team room to
    facilitate communication and collaboration.
  \end{itemize}
  Skills: \emph{Agile / XP, Soar, C++, Ruby, GOMSL}
}

\cventry {May 2002--\\July 2005} {Research Engineer} {Oasis Advanced Engineering} {Auburn Hills, Michigan} {} {%
  Oasis develops hardware and software for advanced military training systems,
  including technology that embeds training devices into fielded
  vehicles. These devices allow crews to train while deployed, where normally
  their skills decline.\newline While at Oasis, I:
  \begin{itemize}
  \item Participated in the development of a safety-critical base
    operating system. The system was targeted for the Visual Display
    Unit used to monitor a nuclear power plant. The code followed the
    strict guidelines of the Nuclear Regulatory Commission for
    software safety.
  \item Participated in the implementation of several versions of the
    Abrams Common Software Library (ACSL) and Wolverine Common
    Software Library (WCSL). These projects entail the conversion of
    vehicle software for use in all M1A2 Main Battle Tank, M1A2 SEP
    Main Battle Tank, and Wolverine Mobile Bridge Deployment System
    training devices. The functionality of the vehicles' embedded
    operating systems, graphics systems, and communication bus are
    preserved in a UNIX operating system environment.
  \end{itemize}
  Skills: \emph{Ada, C, C++, Java, Perl, Php, Ruby}
}

%% \cventry {Summer 2001} {Associate Research Engineer}
%%          {Oasis Advanced Engineering} {Auburn Hills, Michigan} {}
%% {
%%   During this educational summer internship, I:
%%   \begin{itemize}
%%   \item Participated in the initial development of the Wolverine
%%     Common Software Library (WCSL).
%%   \item Developed, as part of a team, the Digital Display Tabletop
%%     Trainer Wolverine variant (D2T2-W).  This version of the
%%     D2T2 system utilizes the Wolverine Common Software Library
%%     to provide a vehicle display trainer on a desktop PC.
%%   \end{itemize}
%% }

% \pagebreak
\section{Education}
\cventry {2002} {Bachelor of Science, Computer Science with Honors} {Michigan State University} {East Lansing, Michigan} {} {}
%% \cventry {1993} {63H10 Tracked Vehicle Maintenance Training} {U.S. Army Ordnance Training Center} {Aberdeen, Maryland} {} {}

\section{Military Service}
\cventry {1995--2000} {Michigan Army National Guard} {\newline1070th Maintenance Company} {Lansing, Michigan} {} {}
\cventry {1992--1995} {United States Army} {1st Infantry Division} {Fort Riley, Kansas} {} {}

\end{document}
